\documentclass[sigconf]{acmart}

\usepackage{booktabs} % For formal tables
\usepackage{amsmath}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage[T1]{fontenc}
\usepackage{tabularx}
\usepackage{array}
%\usepackage{txfonts}
\usepackage{pbox}
\usepackage{subfig}
\usepackage{graphicx}
\usepackage{mathtools}
\DeclarePairedDelimiter\ceil{\lceil}{\rceil}
\DeclarePairedDelimiter\floor{\lfloor}{\rfloor}

\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}


% Copyright
%\setcopyright{none}
%\setcopyright{acmcopyright}
%\setcopyright{acmlicensed}
\setcopyright{rightsretained}
%\setcopyright{usgov}
%\setcopyright{usgovmixed}
%\setcopyright{cagov}
%\setcopyright{cagovmixed}


\graphicspath{{images/}}

% DOI
\acmDOI{10.475/123_4}

% ISBN
\acmISBN{123-4567-24-567/08/06}

%Conference
\acmConference[GECCO '18]{the Genetic and Evolutionary Computation Conference 2018}{July 15--19, 2018}{Kyoto, Japan}
\acmYear{2018}
\copyrightyear{2018}

\acmPrice{15.00}


\begin{document}
\title{The influence of fitness caching on modern evolutionary methods and fair computation load measurement}

\author{Michal W. Przewozniczek}
\affiliation{%
	\institution{Department of Computational Intelligence}
	\institution{Wroclaw University of Science and Technology}
	\city{Wroclaw}
	\country{Poland} 
}
\email{michal.przewozniczek@pwr.edu.pl}

\author{Marcin M. Komarnicki}
\affiliation{%
  \institution{Department of Computational Intelligence}
  \institution{Wroclaw University of Science and Technology}
  \city{Wroclaw}
  \country{Poland} 
}
\email{marcin.komarnicki@pwr.edu.pl}



\begin{abstract}
	
Any evolutionary method may store the fitness values for the genotypes it has already rated. Any time the fitness is to be computed, the check may be made if the fitness for the same genotype was not computed earlier. If so, then instead of re-evaluating the same genotype, the stored value from the repository may be returned. Such technique will be denoted as fitness caching. It is easy to implement in any evolutionary method, and it minimizes the number of fitness function evaluations (FFE), which is desirable. Despite its simplicity fitness caching may significantly affect the computation load spent on fitness computation. Moreover, it may cause that the FFE will not be a reliable computation load measure. Depending on the method and the solved problem the costs and benefits brought by fitness caching may significantly differ. Therefore, in this paper, we analyze its influence on the state-of-the-art evolutionary methods. The research is based on the theoretical problems and shows different phenomena caused by fitness caching. Finally, we show that this technique may be used for reaching far more sophisticated objectives (e.g., dynamic population size management) than a simple FFE minimization.

\end{abstract}

%
% The code below should be generated by the tool at
% http://dl.acm.org/ccs.cfm
% Please copy and paste the code instead of the example below. 
%
 \begin{CCSXML}
	<ccs2012>
		<concept>
			<concept_id>10010147.10010178</concept_id>
			<concept_desc>Computing methodologies~Artificial intelligence</concept_desc>
			<concept_significance>500</concept_significance>
		</concept>
	</ccs2012>
\end{CCSXML}

\ccsdesc[500]{Computing methodologies~Artificial intelligence}

% We no longer use \terms command
%\terms{Theory}

\keywords{Fitness Function Evaluations Number Minimization, Genetic Algorithms, Computation Load Measurement}


\maketitle

\input{FtinessCachingBody}

\bibliographystyle{ACM-Reference-Format}
\bibliography{sigproc} 


\end{document}
